Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-03 sections/discussion.tex
shorten reference, and comment one subsection of discussion

% !TEX root = ../paper.tex
\section{Discussion}
Our results have shown that using semantic similarity can classify the usefulness of comments
and that our approach can also reduce human effort and error proneness of manual classification.
Besides the results, we also found interesting findings in our case study.
We discuss these findings as follows:

@@

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
\subsection{What decisions are made during the manual classification?}
During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes. We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters. For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g. Git and Gerrit).
%During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
%
%\begin{itemize}
%	\item they contain new information;
%	\item they contain constructive suggestions;
%	\item they discuss directly about the change; and
%	\item they discuss technical matters.
%\end{itemize}
%
%Examples of reasons for negative comments include:
%
%\begin{itemize}
%	\item chatting (i.e. no new information, just communication);
%	\item not discussing directly about the change;
%	\item discussing about the process workflow; and
%	\item discussing about Git or Gerrit itself.
%\end{itemize}

>>>>

% !TEX root = ../paper.tex
\section{Discussion}
%Our results have shown that using semantic similarity can classify the usefulness of comments
%and that our approach can also reduce human effort and error proneness of manual classification.
%Besides the results, we also found interesting findings in our case study.
%We discuss these findings as follows:

@@

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful

%\subsection{What decisions are made during the manual classification?}
%During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes. We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters. For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g. Git and Gerrit).

%During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
%
%\begin{itemize}
%	\item they contain new information;
%	\item they contain constructive suggestions;
%	\item they discuss directly about the change; and
%	\item they discuss technical matters.
%\end{itemize}
%
%Examples of reasons for negative comments include:
%
%\begin{itemize}
%	\item chatting (i.e. no new information, just communication);
%	\item not discussing directly about the change;
%	\item discussing about the process workflow; and
%	\item discussing about Git or Gerrit itself.
%\end{itemize}

### 2014-08-03 sections/results.tex
shorten reference, and comment one subsection of discussion

According to our results, we can answer RQ1 as follows: \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random classifier.}

@@

\textbf{Cost Efficiency:}
% briefly explain
We determined cost efficiency in terms of time use for manual assessment.
For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
However, this time may be inaccurate since practitioners did not make assessments under a controlled environment.

% nitty-gritty details
To be more precise, we considered only the time interval between two votes that are not more than 10 minutes apart.
The average time interval between votes is 28 seconds.
Thus, for 318 comments, the assessment time should be 7.42 person hours.
Using the same average interval time for all 10,583 comments,
we can imply that the manual assessment time would be 82.3 person hours.

% how our model helps
When applying our approach to classify these all comments, the models left only 23.5\% of comments for manual assessment (undetermined comments) as shown in Table \ref{tb:percent}.
This means that only 19.34 person hours of additional manual assessment of these undermined comments are needed, thus saving 76.5\% of human effort.

>>>>

%According to our results, we can answer RQ1 as follows: \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random classifier.}

@@

\textbf{Cost Efficiency:}
% briefly explain
We determined cost efficiency in terms of time use for manual assessment.
%For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
%However, this time may be inaccurate since practitioners did not make assessments under a controlled environment.
% nitty-gritty details
%To be more precise, 
We considered only the time interval between two votes that are not more than 10 minutes apart since  practitioners did not make assessments under a controlled environment.
The average time interval between votes is 28 seconds.
Thus, for 318 comments, the assessment time should be 7.42 person hours.
Using the same average interval time for all 10,583 comments,
we can imply that the manual assessment time would be 82.3 person hours.
% how our model helps
When applying our approach to classify these all comments, the models left only 23.5\% of comments for manual assessment (undetermined comments) as shown in Table \ref{tb:percent}.
This means that only 19.34 person hours of additional manual assessment of these undermined comments are needed, thus saving 76.5\% of human effort.
